Handling String-Number Conversion in String Constraint Solving

### 2019-11-06 draft.tex
some misc changes

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\sti}[1]{\mbox{\textbf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textbf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
\newcommand{\modelof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}

@@

For example, in the example of Figure~\ref{fig:sfa_def}, 
from $\parikhof x(v_0) = \parikhof x(v_1) = \cdots = \parikhof x(v_{m-1})=1$ and $\parikhof x(v^0_1)=\parikhof x(v^1_1)=\parikhof x(v^2_1)=2$, then $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
\todo{add Presburger constraints to allow more expressive power.}

@@

\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}

>>>>

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\sti}[1]{\mbox{\textbf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textbf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
\newcommand{\modelof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}

@@

For example, in the example of Figure~\ref{fig:sfa_def}, 
from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
\todo{add Presburger constraints to allow more expressive power.}

%For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string. For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted. Moreover, from $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$, we can derive $w=v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ by exploring the automata structure. \todo{add Presburger constraints to allow more expressive power.}

@@

%\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
\section{Flat Underapproximation for Equalities and Regular Constraints} \label{section:eq}
